---
title: "Vignette Package3"
author: "Joanna Przybyl"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.height = 4,
  fig.width = 7,
  fig.align = "center",
  cache = FALSE
)
```
# Executive Summary

## Introduction

We aimed to compare the number of mutations found in ARID1A tumor suppressor gene across different tumor types included in The Cancer Genome Atlas.

## Methods

We downloaded the mutation data from Tumor Portal website (http://www.tumorportal.org/view?geneSymbol=ARID1A) on July 18, 2016.
Downloaded data are in .maf file which we converted into .csv file to make the input suitable for R.

We used dplyr to summarize the number of ARID1A mutations per tumor type.
We used package pplot2 to plot the summarized number of mutations per tumor type.

## Results

We observed that the highest number of ARID1A mutations were present in endometrial carcinoma (UCEC).

```{r}
library(ggplot2)
library(dplyr)
library(Package3)
pplot(ARIDA1)
```

## Conclusions

Frequncy of ARID1A mutations differ between tumor types.

