---
title: "How_to_write_a_package"
author: "Joanna Przybyl"
date: "July 18, 2016"
output: html_document
---

```{r}
# First load the following packages
library(devtools)
library(roxygen2)
library(knitr)
library(rmarkdown)
```



```{r}
#Set the working drectory to the appropriate folder
setwd("~/Desktop/SISBID_Module3/package3")

#Create a package in this directory
devtools::create("Package3")

#This creates a new folder (toyPackage) populated with some of the files every package needs.

#What is there?
#.gitignore
#.Rbuildignore
#DESCRIPTION
#NAMESPACE
#R/ (initially empty)
#Package3.Rproj

# First edit the DESCRIPTION file
# Change the title, version, description, the author, license infor etc.
# License options:
# 1. CC0 (Creative Commons) is extremely broad; other
# commonly used ones are
# 2. MIT and
# 3. GPL (please see cheatsheet).

# Now document all of the changes in the package
# updates NAMESPACE, creates man/,
# edits DESCRIPTION

document()
build()
install()
check()
.rs.restartR()
library(Package3)
```

# Next step
# add is more text documenting what we want the package to do.
# Create a new R script, wrote some description and save it ro the R forlder
# include a name and a doc type in this R script starting with @
# After you do this, document all of the changes again



```{r}
document()
build()
install()
check()
.rs.restartR()
```

# Invoking document() now generated an R documentation (.Rd) file in man/

# ?Package3 will now check the documentation for the package

```{r}
library(Package3)
?Package3
```

# Some stuff to be included in the package:
# README.md
# vignettes
# data

# Use these commands:

```{r}
use_readme_rmd() # creates a markdown
use_vignette("Package3_vignette") # this will create a vignette for the package (you need to add a name)
```

# Go through the document - build - install - check cycle again to save all of the changes

```{r}
document()
build()
install()
check()
.rs.restartR()
```

```{r}
library(Package3)
```

# Now we can add a trivial function to this package
# Create new R script, insert the function and save it to the R folder

#After creating a function called trivial, go through this loop again:

```{r}
document()
build()
install()
check()
.rs.restartR()
```

```{r}
library(Package3)
?trivial2
```

# Add some data to the package
```{r}
ARID1A <- read.csv("ARID1A.csv")
use_data(ARID1A) #saves the data to the package
```

#After adding ARID1A data, go through this loop again:

```{r}
document()
build()
install()
check()
.rs.restartR()
```

```{r}
library(Package3)
```

# Now add a new function to generate a plot from ARID1A data
# In a new R script file


# Adding a dependent package to be loaded together with my package
```{r}
use_package(package, type=Imports, pkg=".")
```